Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
Updates from Overleaf
adv-cor-plot inserted to discuss the correlation.
adv-cor-plot explnation paragraph.

\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{7cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Households using an improved water source
 & Percentage of households whose main source of drinking water is an improved source.
 \\\hline
  \texttt{pipy} & Households using water piped into yard/plot
& Percentage of households whose main source of drinking water is water piped into the yard or plot.
\\\hline
 \texttt{truc} & Households using tanker truck & Percentage of households whose main source of drinking water is tanker truck.
\\\hline
 \texttt{ctan} & Households using cart with tank & Percentage of households whose main source of drinking water is cart with tank.
\\\hline
 \texttt{bott} & Households using bottled water & Percentage of households whose main source of drinking water is bottled water/demi john.
\\\hline
 \texttt{uiws} & Households using an unimproved water source & Percentage of households whose main source of drinking water is an unimproved source.
\\\hline
 \texttt{othw} & Households using other water source & Percentage of households whose main source of drinking water is other.
\\\hline
 \texttt{iwsp} & Households with improved water source on the premises & Percentage of the de jure population living in households with an improved water source on the premises.
\\\hline
 \texttt{basw} & Households with basic water service
 & Percentage of households with basic water service, defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\hline
 \texttt{liws} & Households with limited water service
 & Percentage of households with limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\hline
 \texttt{prem} & Households with water on the premises
 & Percentage of households with water on the premises.
\\\hline
 \texttt{bicy} & Households possessing a bicycle
 & Percentage of households possessing a bicycle.
\\\hline
 \texttt{acar} & Households possessing an animal drawn cart
 & Percentage of households possessing an animal drawn cart.
\\\hline
 \texttt{mcyc} & Households possessing a motorcycle
 & Percentage of households possessing a motorcycle.
\\\hline
 \texttt{pcar} & Households possessing a private car
 & Percentage of households possessing a private car.
\\\hline
 \texttt{boat} & Households possessing a boat with a motor
 & Percentage of households possessing a boat with a motor.
\\\hline
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
\\\hline
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (national averages at household level)}
  \label{tab:summary}
\end{table}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}

>>>>

\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{5cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Households using an improved water source
 & Percentage of households whose main source of drinking water is an improved source.
 \\\hline
  \texttt{pipy} & Households using water piped into yard/plot
& Percentage of households whose main source of drinking water is water piped into the yard or plot.
\\\hline
 \texttt{truc} & Households using tanker truck & Percentage of households whose main source of drinking water is tanker truck.
\\\hline
 \texttt{ctan} & Households using cart with tank & Percentage of households whose main source of drinking water is cart with tank.
\\\hline
 \texttt{bott} & Households using bottled water & Percentage of households whose main source of drinking water is bottled water/demi john.
\\\hline
 \texttt{uiws} & Households using an unimproved water source & Percentage of households whose main source of drinking water is an unimproved source.
\\\hline
 \texttt{othw} & Households using other water source & Percentage of households whose main source of drinking water is other.
\\\hline
 \texttt{iwsp} & Households with improved water source on the premises & Percentage of the de jure population living in households with an improved water source on the premises.
\\\hline
 \texttt{basw} & Households with basic water service
 & Percentage of households with basic water service, defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\hline
 \texttt{liws} & Households with limited water service
 & Percentage of households with limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\hline
 \texttt{prem} & Households with water on the premises
 & Percentage of households with water on the premises.
\\\hline
 \texttt{bicy} & Households possessing a bicycle
 & Percentage of households possessing a bicycle.
\\\hline
 \texttt{acar} & Households possessing an animal drawn cart
 & Percentage of households possessing an animal drawn cart.
\\\hline
 \texttt{mcyc} & Households possessing a motorcycle
 & Percentage of households possessing a motorcycle.
\\\hline
 \texttt{pcar} & Households possessing a private car
 & Percentage of households possessing a private car.
\\\hline
 \texttt{boat} & Households possessing a boat with a motor
 & Percentage of households possessing a boat with a motor.
\\\hline
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
\\\hline
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (national averages at household level)}
  \label{tab:summary}
\end{table}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
As we continued to study further upon the correlations of the variables, we used more advanced correlation graphs to determined their p value and to see relationship between different categorical variables is shown in Figure 3, which again indicates greater detailed comparison between the variables. Households with improved water source on the premises (iwsp) has strong relationship with  households with basic water service (basw) of .84 and p value of less than 0.001. Also, we learned and discovered that Households using an unimproved water source (uiws) have a positive relationship with Households using an unprotected well water (uwel), Households using an unprotected spring (uspr), and Households using surface water (surw) with p value of less than 0.001 as well. These relationships justify the necessity to research further if the particular water accessibility variables can increase accessibility of particular water sources in order to reach the universal access to water by 2030, as proposed in the SDGs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
